---
title: "missing-igraph-dependency"
author: "Calum Webb"
date: '2022-09-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Remove packages for testing.

```{r}

remove.packages(c("igraph", "astatur"))

# Restart R

```

Try installing astatur package from Github repo

```{r}

# Package cloned from github 23/09/2022
devtools::install_github("ihrke/astatur")

```

Output:

    * installing *source* package ‘astatur’ ...
    ** using staged installation
    ** R
    ** data
    *** moving datasets to lazyload DB
    ** inst
    ** byte-compile and prepare package for lazy loading
    Error : package or namespace load failed for ‘semPlot’ in loadNamespace(i, c(lib.loc, .libPaths()), versionCheck = vI[[i]]):
     there is no package called ‘igraph’
    Error: unable to load R code in package ‘astatur’
    Execution halted
    ERROR: lazy loading failed for package ‘astatur’
    * removing ‘/Library/Frameworks/R.framework/Versions/4.0/Resources/library/astatur’
    Warning in install.packages :
      installation of package ‘/Users/calumwebb/Library/Mobile Documents/com~apple~CloudDocs/r/astatur’ had non-zero exit status

Session info

    R version 4.0.4 (2021-02-15)
    Platform: x86_64-apple-darwin17.0 (64-bit)
    Running under: macOS 12.5.1
    
    Matrix products: default
    LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib
    
    locale:
    [1] en_GB.UTF-8/en_GB.UTF-8/en_GB.UTF-8/C/en_GB.UTF-8/en_GB.UTF-8
    
    attached base packages:
    [1] stats     graphics  grDevices utils     datasets  methods   base     
    
    loaded via a namespace (and not attached):
     [1] compiler_4.0.4   here_1.0.1       fastmap_1.1.0    rprojroot_2.0.3  cli_3.2.0        htmltools_0.5.2  tools_4.0.4     
     [8] yaml_2.3.5       rmarkdown_2.11.3 knitr_1.40       xfun_0.30        digest_0.6.29    rlang_1.0.2      evaluate_0.16   

After installing package `igraph`

```{r}

# install package igraph from CRAN
install.packages("igraph", type = "binary")

# Package cloned from github 23/09/2022
install.packages(here::here(), repos = NULL, type = "source")

```


After having installed igraph, package installs successfully.

    * installing *source* package ‘astatur’ ...
    ** using staged installation
    ** R
    ** data
    *** moving datasets to lazyload DB
    ** inst
    ** byte-compile and prepare package for lazy loading
    ** help
    *** installing help indices
    ** building package indices
    ** testing if installed package can be loaded from temporary location
    ** testing if installed package can be loaded from final location
    ** testing if installed package keeps a record of temporary installation path
    * DONE (astatur)

Try change to DESCRIPTION to add igraph as a dependency

```{r}

remove.packages(c("igraph", "astatur"))

# Restart R

# Package cloned from github 23/09/2022
install.packages(here::here(), repos = NULL, type = "source", dependencies = TRUE)

```


